---
title: "Yiya Course 3 Learner Outcome Regressions"
author: "Ren Butler"
date: "2023-11-03"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
## Regression of Outcomes

```{r}
learner_outcomes = read.csv("/Users/ddbutler/repos_new/yiya_data_analysis/data/processed/course_3_outcomes_paid_users.csv")

#ensure course_id is treated as a factor
learner_outcomes$course_id = factor(learner_outcomes$course_id)
```


```{r}
#predicting exam performance, with # of questions during the broadcast and the registration cluster, with interaction
summary(lm(eqc_fa_sr ~ pqfa_db * course_id, data = learner_outcomes))
```