---
title: "lira_learner_outcomes_analysis"
author: "Ren Butler"
date: "2023-10-04"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("broom")
#install.packages("ggpubr")
```
```{r}
library(ggplot2)
library(dplyr)
library(broom)
library(ggpubr)
```
```{r}
# read data
lira_learner_outcomes = read.csv("/Users/ddbutler/repos_new/yiya_data_analysis/data/processed/lira_learner_outcomes.csv")
```

## Exploratory Data Analysis
```{r}
summary(lira_learner_outcomes)
```
# Assumption Checking

## Independence of Observations

We assume the explanatory variables are independent (not highly correlated). The correlation is 0.29 on the (-1 to 1) scale so I accept this assumption of independence.
```{r}
cor(lira_learner_outcomes$total_practice_questions_during_broadcasts, lira_learner_outcomes$total_practice_questions_before_after_broadcasts)
```

## Normality

Normality does not hold true for either variables. (No bell shape)

```{r}
hist(lira_learner_outcomes$total_practice_questions_during_broadcasts, main="Distribution of Practice Questions During Broadcast", xlab = "Total First Time Responses to Lesson Questions During Broadcasts")
```

```{r}
hist(lira_learner_outcomes$total_practice_questions_before_after_broadcasts, main="Distribution of Practice Questions During Broadcast", xlab = "Total First Time Responses to Lesson Questions Outside Broadcasts")
```

## Linearity
```{r}
plot(total ~ total_practice_questions_during_broadcasts, data=heart.data)
```


## Linear Regression

Linear regression is a regression model that uses a straight line to describe the **relationship between variables**. It finds the line of best fit through your data by searching for the value of the regression coefficient(s) that minimizes the total error of the model.

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

